Accuracy and stability for elliptic operators in a finite volume context

### 2023-06-29 example/EBCM/hoeb_petsc/_doc/paper.tex
gearing up for EBCM petsc solver

@@

>>>>

\section{Truncation error convergence rates}

For this family of operators, $P_T$ should be entirely determinative
of the truncation error convergence rate.   For completeness, we
intend to verify this.    But as has been shown,
for aggressive choices of $P_T$ and $P_W$ the system matrix can be
poorly conditioned, leading to some degree of uncertainty about the
stencil coefficients.
In this section, we also explore how these conditioning issues affect the
measured truncation error of the operator.

@@

\section{Solution error convergence rates}
